\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{amsmath}


\usepackage[hmargin=3cm,vmargin=6.0cm]{geometry}
\topmargin=-2cm
\addtolength{\textheight}{6.5cm}
\addtolength{\textwidth}{2.0cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\evensidemargin}{0.0cm}
\usepackage{indentfirst}
\usepackage{amsfonts}

\begin{document}

\section*{Student Information}

Name :Aybüke Aksoy\\

ID :2448090 \\


\section*{Answer 1}
\paragraph{
Given a sample of data and a desired confidence level $(1-\alpha)$, we can construct a confidence interval [a,b] that will satisfy the condition:
\[P\{a \leq \theta \leq b\}=1-\alpha\]
We can start by estimating $\theta$.\\
Standardizing the unbiased estimator $\hat{\theta}$ with normal distribution, we get:
\[Z=\frac{\hat{\theta}-E(\hat{\theta})}{\sigma(\hat{\theta})}=\frac{\hat{\theta}-\theta}{\sigma(\hat{\theta})}\]
This variable falls between $-z_{\alpha/2}$ and $z_{\alpha/2}$ with the probability $(1-\alpha)$
\[P\{-z_{\alpha/2} \leq \frac{\hat{\theta}-\theta}{\sigma(\hat{\theta})} \leq z_{\alpha/2}\}=1-\alpha\]
Solving the inequality for $\theta$, we get:
\[a=\hat{\theta}-z_{\alpha/2}\sigma(\hat{\theta})\]
\[b=\hat{\theta}+z_{\alpha/2}\sigma(\hat{\theta})\]
While estimating the population mean $\hat{X}$:\\
\[\hat{\theta}=\hat{X}\]
\[a=\hat{X}-z_{\alpha/2}\frac{\sigma}{\sqrt{n}}\]
\[b=\hat{X}+z_{\alpha/2}\frac{\sigma}{\sqrt{n}}\]
}
\paragraph{a)
\[Standard \ deviation :\sigma=3\]
\[Sample \ size : n=10\]
\[Sample \ mean : \hat{X}=\frac{20.1+12.8+18.9+16.4+20.3+10.1+15.4+12.4+24.7+18.5}{10}=16.96\]
\[Confidence \ level1 : 1-\alpha=0.90 \ ,\ \alpha=0.1\]
\[Confidence \ level2 : 1-\alpha=0.99 \ ,\ \alpha=0.01\]
From the table:
\[z_{0.05}=1.645\]
We can find a and b for $\%90$ confidence level as:
\[a=16.96-1.645\frac{3}{\sqrt{10}}=15.4\]
\[b=16.96+1.645\frac{3}{\sqrt{10}}=18.521\]
\[Confidence \ interval : [15.4,18.521]\]
From the table:
\[z_{0.005}=2.576\]
We can find a and b for $\%99$ confidence level as:
\[a=16.96-2.576\frac{3}{\sqrt{10}}=15.4\]
\[b=16.96+2.576\frac{3}{\sqrt{10}}=18.521\]
\[Confidence \ interval : [14.517,19.403]\]
}

\paragraph{b)
\[Confidence \ level : 1-\alpha=0.98 \ ,\ \alpha=0.02\]
\[margin : z_{\alpha/2}\frac{\sigma}{\sqrt{n}}=1.55\]
Hence;
\[Sample \ size : n \geq (z_{\alpha/2}\frac{\sigma}{1.55})^2\]
From the table:
\[z_{0.01}=2.326\]
\[n \geq (2.326\frac{3}{1.55})^2\]
\[n \geq 20.267\]
\[n=21\]
}


\section*{Answer 2}
\paragraph{a)
No. The mean rating and sample size are not enough for statistics of a restaurant. We also need sample for standard deviation and variance. 
}
\paragraph{b)
\[H_0= \ the \ null \ hypothesis\]
\[H_A= \ the \ alternative \ hypothesis \]
Since we decide whether a restaurant will be included in our list of candidate restaurants or not from looking at the rating being lower than 7.5 with $\%5$ level of significance, we can determine our null hypothesis as:
\[H_0: \mu_0=7.5\]
\[H_A: \mu_0 < 7.5\]
A normally would not be in our list because its rating is 7.4; however, if we have enough evidence to reject the null hypothesis, which is also in favor of $H_A$, A can not be in our list. 
To decide, we can use the Z test:
$H_A$ is a left tail alternative. 
A level $\alpha$ test with a left-tail alternative should:
\[reject \  H_0, \ \ \ \ if \ Z \ \leq -z_\alpha\]
\[accept \  H_0, \ \ \ \ if \ Z \ > -z_\alpha\]
In this case, the rejection region is consists of small values of Z only. 
\[A=[-z_\alpha, + \infty)\]
\[R=[- \infty, -z_\alpha)\]
For an estimator $\hat{\theta}$ for population parameter $\theta$ that has normal distribution:
\[Test \ Statistic: Z=\frac{\hat{\theta}-E(\hat{\theta})}{\sqrt{Var(\hat{\theta})}}=\frac{\hat{X}-\mu_0}{\sigma/\sqrt{n}}\]
\[Standard \ deviation :\sigma=0.8\]
\[Sample \ size : n=256\]
\[Sample \ mean : \hat{X}=7.4\]
\[\alpha=0.05\]
\[z_\alpha=1.645\]
Hence,
\[Z=\frac{7.4-7.5}{0.8/\sqrt{256}}=-2\]
Since $Z<-z_\alpha$, we can reject the null hypothesis.\\ 
Thus, the restaurant A is not included in the list.
}
\paragraph{c)
Using the information in part b with the only difference which is taking $\sigma$ as 1.0 instead of 0.8 and calculating Z again:
\[Z=\frac{7.4-7.5}{1.0/\sqrt{256}}=-1.6\]
Since $Z>-z_\alpha$, we should accept the null hypothesis.\\ 
Thus, the restaurant A is included in the list.}
\paragraph{d)
Since the mean of user ratings for restaurant A=7.6 is already greater than $\mu_0=7.5$, our decision will not be affected by other parameters like standard deviation. Hence, we do not have to conduct any statistical test. 
}
\section*{Answer 3}
\paragraph{
If we have enough evidence to reject the null hypothesis, which is also in favor of $H_A$, we can claim that there is not at least 90 minutes run-time improvement.\\
Hence we can take $H_0$ and $H_A$ as:
\[H_0: \mu_A-\mu_B = 90\]
\[H_A:\mu_A-\mu_B < 90\]
Computer A:
\[Sample \ Standard \ deviation :\sigma_A=5.2\]
\[Sample \ size : n=20\]
\[Sample \ mean : \hat{A}=211\]
Computer B:
\[Sample \ Standard \ deviation :\sigma_B=22.8\]
\[Sample \ size : m=32\]
\[Sample \ mean : \hat{B}=133\]
To decide, we can use the T test:\\
}
\paragraph{a)
\[reject \  H_0, \ \ \ if \ t \leq -t_\alpha\]
\[accept \  H_0, \ \ \ if \ t > -t_\alpha\]
While population variances are equal:\\
\[\alpha=0.01\]
\[\sigma_{A}^{2}=\sigma_{b}^{2}=\sigma_^{2}\]
\[Pooled \ Sample \ Variance: s_p^2= \frac{(n-1)\sigma_{A}^{2}+(m-1)\sigma_{B}^{2}}{n+m-2} \]
\[Degree \ of \ freedom: n+m-2\]
\[t= \frac{\hat{A}-\hat{B}-D}{s_p\sqrt{\frac{1}{n}+\frac{1}{m}}} \]
\[s_p^2= \frac{19*5.2^{2}+31*22.8^{2}}{50}=332.576 \]
\[D=50\]
\[t_\alpha=t_{0.01}=2.403 \ , \ from \ the \ table\]
\[t=\frac{211-133-90}{\sqrt{332.576}\sqrt{\frac{1}{20}+\frac{1}{32}}}=-2.3084 \]
Since $t > -t_\alpha$:\\
We should accept the null hypothesis.\\
Hence, B does provide 90 minutes or better improvement. 
}
\paragraph{b)
While population variances are not equal:\\
\[T \ Ratio: \frac{(\hat{A}-\hat{B})-(\mu_A-\mu_B)}{\sqrt{\frac{s^2_A}{n}+\frac{s^2_B}{m}}} \]
Using the information in part a:
\[T \ Ratio: \frac{(211-133)-90}{\sqrt{\frac{5.2^2}{20}+\frac{22.8^2}{32}}}=-2.8606\]
\[Degrees \ of \ freedom: \frac{(\frac{\sigma_A^2}{n^2}+\frac{\sigma_B^2}{m^2})^2}{\frac{(\sigma_A^2/n)^}{n-1}+\frac{(\sigma_B^2/m)^2}{m-1}}=36 \]
\[t_\alpha=t_{0.01}=2.434 \ , \ from \ the \ table\]
Since $t < -t_\alpha$:\\
We should reject the null hypothesis.\\
Hence, B does not provide 90 minutes or better improvement. 

}



\end{document}

